---
title: 'Innovation and Development: Bibliometrics Analysis'
author: "Marija Rakas (rakas@business.aau.dk)"
date: "Updated `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    code_folding: hide
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
    theme: flatly
---

```{r setup, include=FALSE}
### Generic preamble
rm(list=ls())
Sys.setenv(LANG = "en") # For english language
options(scipen = 5) # To deactivate annoying scientific number notation

### Knitr options
library(knitr) # For display of the markdown
knitr::opts_chunk$set(warning=FALSE,
                     message=FALSE,
                     comment=FALSE, 
                     fig.align="center"
                     )
```

```{r}
### Load standardpackages
library(tidyverse) # Collection of all the good stuff like dplyr, ggplot2 ect.
library(magrittr) # For extra-piping operators (eg. %<>%)
library(bibliometrix)
library(kableExtra)
```

# Data & Preprocessing

## Corpus Creation
1. Scopus download of documents retrieved from search strings from Lorentzen (2010). Limited to `LANGUAGE = ENGLISH AND TYPE = (ARTICLE) AND SRCTYPE=(JOURNAL)`. Scopus1 is created from searching all Scopus's subject areas, and applying additional filtering on the resulting set of 6933 publications. Namely,I performed second filtering based on search string 'product OR process OR organisational innovation or institution*. This type of criteria is applied manually in Lorentzen (2010). Scopus2 and Scopus3 are generated without second filtering. Scopus2 is limited to social science subject areas, whereas Scopus3 is limited to social science subject areas, excluding Art&Humanities and Psychology. 
2. WoS download of documents retrieved from search string from Lorentzen (2010). Limited to `LANGUAGE = ENGLISH AND TYPE = (ARTICLE) AND SRCTYPE=(JOURNAL)`. For wos1 same limitations as in Scopus1.That lead to initial 5142 publications. Wos2 is limited to Social Sciences Citation Index (SSCI) --1956-present, and no second filtering is applied.  

That leads to following corpus sizes:

```{r}

file_scopus1<- "../data/scopus1.csv"
file_scopus2<-c("../data/scopus21.csv", "../data/scopus22.csv", "../data/scopus23.csv")
file_scopus3<-c("../data/scopus31.csv", "../data/scopus32.csv", "../data/scopus33.csv")

file_wos1 <- c("../data/wos11.txt","../data/wos12.txt" )
file_wos2 <- c("../data/wos21.txt","../data/wos22.txt","../data/wos23.txt", "../data/wos24.txt","../data/wos25.txt","../data/wos26.txt", "../data/wos27.txt")

M_scopus1 <- convert2df(file_scopus1, dbsource = "scopus", format = "csv")
M_scopus2 <- convert2df(file_scopus2, dbsource = "scopus", format = "csv")
M_scopus3 <- convert2df(file_scopus3, dbsource = "scopus", format = "csv")

M_wos1 <- convert2df(file_wos1, dbsource = "wos", format = "plaintext")
M_wos2 <- convert2df(file_wos2, dbsource = "wos", format = "plaintext")
```


```{r}
cat("Number of publications in scopus1: ", nrow(M_scopus1))
cat("Number of publications in scopus2: ", nrow(M_scopus2)) 
cat("Number of publications in scopus3: ", nrow(M_scopus3))
cat("Number of publications in wos1: ", nrow(M_wos1))
cat("Number of publications in wos2: ", nrow(M_wos2))
```

## Preprocessing

### Genral cleaning
```{r}
# Filtering out unrelated journals
M_wos2 %<>% 
  filter(!(JI %in% c('LANCET', 'PLOS MED.'))) %>%
  as.data.frame()
```

### Identifying countries

```{r}
country_list <- c("Afghanistan", "Burkina Faso" ,  "Burundi" ,  "Central African Republic" ,  "Chad" ,  "Congo" ,  "Eritrea" ,  "Ethiopia" ,  "Gambia" ,  "Guinea" ,  "Guinea-Bissau" ,  "Haiti" ,  "Democratic People's Republic Korea" ,  "Liberia" ,  "Madagascar" ,  "Malawi" ,  "Mali" ,  "Mozambique" ,  "Niger" ,  "Rwanda" ,  "Sierra Leone" ,  "Somalia" ,  "South Sudan" ,  "Sudan" ,  "Syrian Arab Republic" ,  "Tajikistan" ,  "Togo" ,  "Uganda" ,  "Yemen") %>% str_to_lower()
```


```{r}
countries_wos2 <- M_wos2 %>%
  mutate(text = paste(TI, AB, DE, ID, sep = ' ') %>% str_to_lower()) %>%
  mutate(countries = text %>% str_extract_all(paste(country_list, collapse="|")) ) %>%
  select(UT, countries) %>%
  unnest(countries) %>%
  distinct(UT, countries) %>%
  nest(countries) %>% 
  rename(countries = data) %>%
  rowwise() %>%
    mutate(n_countries = countries %>% nrow()) %>%
  ungroup()
```

```{r}
M_wos2 %<>%
  left_join(countries_wos2, by = 'UT')
```

```{r}
M_wos2 %<>%
  replace_na(list('n_countries' = 0))
```

```{r}
M_wos2 %>%
  select(UT, countries, n_countries) %>%
  unnest(countries) %>%
  group_by(countries) %>%
  summarise(n = n(),
            n_frac = sum(1/n_countries) %>% round(1)) %>%
  mutate(n_pct = (n / nrow(M_wos2)) %>% round(2)) %>%
  arrange(desc(n))
```


# General overview of the documents in the corpus:Authors, Publications, countries, sources, and keywords {.tabset}

## Overview Scopus1
```{r}
results_scopus1 <-biblioAnalysis(M_scopus1, sep=";")
S_scopus1 <-  summary(object = results_scopus1, k =10 , pause = FALSE)
```

```{r}
plot(x = results_scopus1, k = 10, pause = FALSE)

```

## Overview Scopus3

```{r}
results_scopus3 <-biblioAnalysis(M_scopus3, sep=";")
S_scopus3 <- summary(object = results_scopus3, k =10 , pause = FALSE)
```

```{r}
plot(x = results_scopus3, k = 10, pause = FALSE)
```


## Overview WoS1

```{r}
M_wos1 <- M_wos1 %>%
  filter(PY <= 2019) %>%
  as.data.frame()

# M_wos <- M_wos[M_wos[,"PY"] <= 2019,]
```


```{r}
results_wos1<-biblioAnalysis(M_wos1, sep=";")

options(width=100)
S_wos1 <- summary(object = results_wos1, k = 10, pause = FALSE)

```

```{r}
plot(x = results_wos1, k = 10, pause = FALSE)
```

## Overview WoS2

```{r}
M_wos2 <- M_wos2 %>%
  filter(PY <= 2019) %>%
  as.data.frame()
```

```{r}
results_wos2<-biblioAnalysis(M_wos2, sep=";")
options(width=100)
S_wos2 <- summary(object = results_wos2, k = 10, pause = FALSE)
```

```{r}
plot(x = results_wos2, k = 10, pause = FALSE)
```


# Cited References{.tabset}

## Scopus1

```{r}
CR_scopus1 <- citations(M_scopus1, field = "article", sep = ";")
#cbind(CR_scopus1$Cited[1:10])
```

```{r}
CR_scopus1$Cited %>% as_tibble() %>% head(20) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 8)
```


```{r}
CR_scopus1 <- citations(M_scopus1, field = "author", sep = ";")
cbind(CR_scopus1$Cited[1:10])

```

```{r}
CR_scopus1 <- localCitations(M_scopus1, sep = ";")
CR_scopus1$Authors[1:10,]
CR_scopus1$Papers[1:10,]

```



## Scopus3

```{r}
CR_scopus3<- citations(M_scopus3, field = "article", sep = ";")
#cbind(CR_scopus3$Cited[1:10])
```

```{r}
CR_scopus3$Cited %>% as_tibble() %>% head(20) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 8)
```

```{r}
CR_scopus3 <- citations(M_scopus3, field = "author", sep = ";")
cbind(CR_scopus3$Cited[1:10])
```

```{r}
CR_scopus3 <- localCitations(M_scopus3, sep = ";")
CR_scopus3$Authors[1:10,]
CR_scopus3$Papers[1:10,]
```



## WoS1

```{r}
CR_wos1 <- citations(M_wos1, field = "article", sep = ";")
#cbind(CR_wos$Cited[1:10])

```

```{r}
CR_wos1$Cited %>% as_tibble() %>% head(20) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 8)
```


```{r}
CR_wos1 <- citations(M_wos1, field = "author", sep = ";")
cbind(CR_wos1$Cited[1:10])

```

```{r}
CR_wos1 <- localCitations(M_wos1, sep = ";")
CR_wos1$Authors[1:10,]
CR_wos1$Papers[1:10,]

```

## WoS2

```{r}
CR_wos2 <- citations(M_wos2, field = "article", sep = ";")
#cbind(CR_wos2$Cited[1:10])

```


```{r}
CR_wos2$Cited %>% as_tibble() %>% head(20) %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 8)
```


```{r}
CR_wos2 <- citations(M_wos2, field = "author", sep = ";")
cbind(CR_wos2$Cited[1:10])

```

```{r}

CR_wos2 <- localCitations(M_wos2, sep = ";")
CR_wos2$Authors[1:10,]
CR_wos2$Papers[1:10,]

```


# Authors, Themes & Journals {.tabset}

## Scopus1

```{r, fig.width=10}
M_scopus1 %>% threeFieldsPlot()
```

## Scopus3

```{r, fig.width=10}
M_scopus3 %>% threeFieldsPlot()
```

## Wos1

```{r}
fig.width=10
M_wos1 %>% threeFieldsPlot()

```

## Wos2

```{r}
fig.width=10
M_wos2 %>% threeFieldsPlot()

```

# Create keyword co-occurrences network & plot the network{.tabset}

## Scopus1

```{r}

NetMatrix_scopus1 <- biblioNetwork(M_scopus1, analysis = "co-occurrences", network = "keywords", sep = ";")

net_scopus1=networkPlot(NetMatrix_scopus1, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)

```

## Scopus3

```{r}

NetMatrix_scopus3 <- biblioNetwork(M_scopus3, analysis = "co-occurrences", network = "keywords", sep = ";")

net_scopus3=networkPlot(NetMatrix_scopus3, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)

```


## Wos1

```{r}
NetMatrix_wos1 <- biblioNetwork(M_wos1, analysis = "co-occurrences", network = "keywords", sep = ";")

net_wos1=networkPlot(NetMatrix_wos1, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)

```

## Wos2

```{r}

NetMatrix_wos2 <- biblioNetwork(M_wos2, analysis = "co-occurrences", network = "keywords", sep = ";")

net_wos2=networkPlot(NetMatrix_wos2, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)

```

# Thematic map based on co-word network analysis and clustering{.tabset}

## Scopus1

```{r}

Map_scopus1=thematicMap(M_scopus1, field = "ID", n = 250, minfreq = 5,
  stemming = FALSE, size = 0.5, n.labels=3, repel = TRUE)
plot(Map_scopus1$map)

```

## Scopus3

```{r}
Map_scopus3=thematicMap(M_scopus3, field = "ID", n = 250, minfreq = 5,
  stemming = FALSE, size = 0.5, n.labels=3, repel = TRUE)
plot(Map_scopus3$map)

```

## WoS1

```{r}
Map_wos1=thematicMap(M_wos1, field = "ID", n = 250, minfreq = 5,
  stemming = FALSE, size = 0.5, n.labels=3, repel = TRUE)
plot(Map_wos1$map)

```

## WoS2

```{r}

Map_wos2=thematicMap(M_wos2, field = "ID", n = 250, minfreq = 5,
  stemming = FALSE, size = 0.5, n.labels=3, repel = TRUE)
plot(Map_wos2$map)

```









